No Dogs On The Couch$_{Base}$

### 2012-11-27 Assignment6/paper/paper.tex
fixed some grammar

This workload is clearly a read-heavy workload that entails no disk writes at
all. Important to note though, this use case may constantly be increasing
(should constantly be increasing for a successful system) and so the load for
this workload may increase quite a bit, and whenever new features are added
there is a potential for a spike in workload.

>>>>

This workload is clearly a read-heavy workload that entails no disk writes at
all. Important to note though, this use case should constantly be increasing in a successful system and so the load for
this workload may increase quite a bit, and whenever new features are added
there is a potential for a spike in this workload.
